Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-04 _03_smoothing_tracks.Rmd
outside panel titles

# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
pal[2] = RColorBrewer::brewer.pal(5, "Blues")[5]
```

@@

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot() +
  geom_point(
    data = data_errors,
    aes(x, y),
    col = pal[3],
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    lwd = 0.5
  ) +
  geom_path(
    data = data_plot,
    aes(x, y,
      col = window_size,
      group = window_size
    ),
    show.legend = F,
    lwd = 0.5
  ) +
  coord_equal(
    expand = F,
    ylim = c(0.6, 0.85),
    xlim = c(NA, 2.3),
    ratio = 1.75
  ) +
  annotate(
    geom = "text",
    x = c(0.75, seq(1.1, 2, length.out = 4)),
    y = 0.82,
    label = sprintf("(%s)", letters[seq(5)]),
    fontface = "bold"
  ) +
  scale_colour_distiller(
    palette = "Blues", direction = 1,
    values = c(-0.5, 1)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )

@@

```{r echo=FALSE}
# prepare data
data_agg_smooth = copy(list_of_agg[[3]]) # 30s aggregate
### plot figures
fig_agg_data_smooth <-
      ggplot(data_agg_smooth) +
        geom_point(
          data = data_agg,
          size = 0.2,
          aes(x, y),
          col = pal[3]
        ) +
        geom_path(aes(x, y),
          col = pal[2],
          lwd = 0.2
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 1,
        size = 2,
        col = pal[2],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank(),
          plot.title = element_text(
            face = "bold",
            margin = margin(t = 30, b = -30),
            hjust = 0.9
          )
        ) +
        coord_cartesian(ylim = c(0.6, NA)) +
        labs(
          title = "(a)"
        )
```

@@

```{r echo=FALSE}
# prepare data
data_agg_error = copy(list_of_agg_errors[[3]]) # 30s aggregate
### plot figures
fig_agg_data_error <-
      ggplot(data_agg_error) +
        geom_point(
          data = data_errors,
          size = 0.1,
          aes(x, y),
          col = "grey"
        ) +
        geom_path(aes(x, y),
          col = pal[2]
          # lwd = 0.1
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 1,
        size = 2,
        col = pal[2],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank(),
          plot.title = element_text(
            face = "bold",
            margin = margin(t = 30, b = -30),
            hjust = 0.9
          )
        ) +
        coord_cartesian(ylim = c(0.6, NA)) +
        labs(
          title = "(b)"
        )
```

@@

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg) +
  geom_hline(
    yintercept =
      1 + quantile(data$speed,
        na.rm = T,
        probs = c(0.5, 0.95)
      ),
    lty = c(1, 2)
  ) +
  geom_errorbar(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      ymin = 1 + median - sd,
      ymax = 1 + median + sd
    ),
    width = 0.2,
    position = position_nudge(x = 0.25)
  ) +
  geom_point(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      y = 1 + median
    ),
    shape = 21,
    size = 3,
    fill = pal[3],
    position = position_nudge(x = 0.25)
  ) +
  geom_boxplot(aes(factor(interval), 1 + speed),
    position = position_nudge(x = -0.25, ),
    fill = "grey",
    alpha = 0.5,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2
  ) +
  scale_y_log10(
    label = scales::comma,
    limits = c(NA, 1.005)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.8
    )
  ) +
  labs(
    x = "interval (s)",
    y = "speed",
    title = "(c)"
  )
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBC"
  )

>>>>

# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
```

@@

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot() +
  geom_point(
    data = data_errors,
    aes(x, y),
    col = pal[3],
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    lwd = 0.5
  ) +
  geom_path(
    data = data_plot,
    aes(x, y,
      col = window_size,
      group = window_size
    ),
    show.legend = F,
    lwd = 0.5
  ) +
  coord_equal(
    expand = F,
    ylim = c(0.6, 0.85),
    xlim = c(NA, 2.3),
    ratio = 1.75
  ) +
  annotate(
    geom = "text",
    x = c(0.75, seq(1.1, 2, length.out = 4)),
    y = 0.82,
    label = sprintf("(%s)", letters[seq(5)]),
    fontface = "bold"
  ) +
  scale_colour_distiller(
    palette = "Purples", direction = 1,
    values = c(-0.5, 1)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )

@@

```{r echo=FALSE}
# prepare data
data_agg_smooth = copy(list_of_agg[[3]]) # 30s aggregate
### plot figures
fig_agg_data_smooth <-
      ggplot(data_agg_smooth) +
        geom_point(
          data = data_agg,
          size = 0.2,
          aes(x, y),
          col = pal[3]
        ) +
        geom_path(aes(x, y),
          col = pal[4],
          lwd = 0.2
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 0,
        size = 2,
        col = pal[4],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank()
        ) +
        coord_cartesian(ylim = c(0.6, NA))
```

@@

```{r echo=FALSE}
# prepare data
data_agg_error = copy(list_of_agg_errors[[3]]) # 30s aggregate
### plot figures
fig_agg_data_error <-
      ggplot(data_agg_error) +
        geom_point(
          data = data_errors,
          size = 0.1,
          aes(x, y),
          col = "grey"
        ) +
        geom_path(aes(x, y),
          col = pal[4]
          # lwd = 0.1
        ) +
        geom_point(aes(x, y,
          group = interval
        ),
        shape = 0,
        size = 2,
        col = pal[4],
        alpha = 1,
        show.legend = F
        ) +
        ggthemes::theme_few() +
        theme(
          axis.text = element_blank(),
          axis.title = element_blank()
        ) +
        coord_cartesian(ylim = c(0.6, NA))
```

@@

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg) +
  geom_hline(
    yintercept =
      1 + quantile(data$speed,
        na.rm = T,
        probs = c(0.5, 0.95)
      ),
    lty = c(1, 2)
  ) +
  geom_errorbar(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      ymin = 1 + median - sd,
      ymax = 1 + median + sd
    ),
    width = 0.2,
    position = position_nudge(x = 0.25)
  ) +
  geom_point(
    data = speed_agg_smooth,
    aes(
      x = factor(interval),
      y = 1 + median
    ),
    shape = 21,
    size = 3,
    fill = pal[3],
    position = position_nudge(x = 0.25)
  ) +
  geom_boxplot(aes(factor(interval), 1 + speed),
    position = position_nudge(x = -0.25, ),
    fill = "grey",
    alpha = 0.5,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2
  ) +
  scale_y_log10(
    label = scales::comma,
    limits = c(NA, 1.005)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    x = "interval (s)",
    y = "speed"
  )
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBC"
  )+
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
  theme(plot.tag = element_text(face = "bold"))
